What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2024-11-25 manuscript.Rmd
final? minor edits for Collabra submission

author:
  - name: Ariel N. James
    affiliation: '1'
    email: ajames2@macalester.edu

@@

    corresponding: yes

@@

    address: 124 Raymond Ave, Poughkeepsie, NY 12604, USA

@@

These data were collected within the context of an undergraduate research methods course. Groups of students (co-authors) designed and programmed experiments in jsPsych, pre-registered their planned analyses, and collected data through Prolific under the supervision of the first author. The OSF repositories associated with these experiments are linked in the methods sections of each individual study. Note that in the current paper we expand on those pre-registered analyses (e.g., including analyses of the calibration quality). All analysis code underlying this paper can be found in the Github repository: https://github.com/jodeleeuw/219-2021-eyetracking-analysis

@@

# Contributions

@@

# Supplemental material

# Data accessibility statement

>>>>

author:
  - name: Ariel N. James
    affiliation: '1'
    role:
      - Conceptualization
      - Formal analysis
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    email: ajames2@macalester.edu
    corresponding: yes
    address: 1600 Grand Ave, Saint Paul, MN 550105, USA

@@

@@

@@

These data were collected within the context of an undergraduate research methods course. Groups of students (co-authors) designed and programmed experiments in jsPsych, pre-registered their planned analyses, and collected data through Prolific under the supervision of the last author. The OSF repositories associated with these experiments are linked in the methods sections of each individual study. Note that in the current paper we expand on those pre-registered analyses (e.g., including analyses of the calibration quality). All analysis code underlying this paper can be found in the Github repository: https://github.com/jodeleeuw/219-2021-eyetracking-analysis

@@

# Contributions
* Joshua R. de Leeuw
    + Conceptualization
    + Data curation
    + Formal analysis
    + Investigation
    + Methodology
    + Project administration
    + Software
    + Supervision
    + Validation
    + Visualization
    + Writing - original draft
    + Writing - review & editing

* Ariel N. James, Rachel Ryskin, and Joshua K. Hartshorne
    + Conceptualization
    + Formal analysis
    + Visualization
    + Writing - original draft
    + Writing - review & editing

* Undergraduate student authors, listed alphabetically: Haylee Backs, Nandeeta Bala, Laila Barcenas-Meade, Samata Bhattarai, Tessa Charles, Gerasimos Copoulos, Claire Coss, Alexander Eisert, Elena Furuhashi, Keara Ginell, Anna Guttman-McCabe, Emma (Chaz) Harrison, Laura Hoban, William A. Hwang, Claire Iannetta, Kristen M. Koenig, Chauncey Lo, Victoria Palone, Gina Pepitone, Margaret Ritzau, Yi Hua Sung, and Lauren Thompson
    + Investigation
    + Methodology
    + Software

@@

# Data accessibility statement
All data and analysis code underlying this paper can be found in the Github repository: https://github.com/jodeleeuw/219-2021-eyetracking-analysis. Study materials and pre-registrations for each experiment are available on Open Science Framework:

* Experiments 1a and 1b: [https://osf.io/g6dum/]
* Experiment 2: [https://osf.io/xezfu/]
* Experiment 3: [https://osf.io/k63b9/]
* Experiment 4: [https://osf.io/x3c49/]
* Experiment 5: [https://osf.io/eubsc/]
